Flowchart of Current Algorithm

### 2009-02-05 docs/flowchart/flowchart.tex
removed Advect Base Pressure and put in calls to enforce_HSE and make_psi

@@

\begin{itemize}
\item Should we eliminate {\bf Advect Base Pressure} entirely, and instead directly
enforce HSE after {\bf Correct Base}?  {\bf Advect Base Pressure} was just a fancy
way of enforcing HSE anyway, so why not just compute the new pressure directly?

@@

\item {\bf Advect Base Pressure}$[p_0^\inp,w_0^\inp,\etarho^\inp] \rightarrow$ 
$[p_0^\outp,\psi^\outp]$\\
is the process by which we update the base state pressure through $\dt$ in time and
compute $\psi$.
\begin{description}

\item[plane-parallel:] First we compute a cell-centered $\psi^\outp$ using
\begin{equation}
 \psi_j^\outp = \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^\inp + \eta_{\rho,j+\myhalf}^\inp\right) g \enskip .
\end{equation}
Then, we discretize the base state pressure evolution equation (paper III; eq.~[31]),
\begin{equation}
\frac{\partial p_0}{\partial t} = 
-w_0 \frac{\partial p_0}{\partial r} + \psi \enskip ,
\label{eq:p0upd_new}
\end{equation}
to compute the new base state pressure,
\begin{equation}
p_{0,j}^\outp = p_{0,j}^\inp - \frac{\dt}{2\dr} \left (w_{0,j+\myhalf}^\inp
+ w_{0,j-\myhalf}^\inp \right)
\left (p_{0,j+\myhalf}^{n+\myhalf} -p_{0,j-\myhalf}^{n+\myhalf} \right ) + \dt \; \psi_j^\outp 
\enskip,
\end{equation}
where the interface states are again found via the procedure described
in paper II, Appendix A.

@@

\item {\bf Advect Base Pressure}$[p_0^{n}, w_0^{\nph,\star}, \etarho^{n+\myhalf,\star}]$ 
$\rightarrow [p_0^{n+1,\star}, \psi^{\nph,\star}]$.

@@

\item {\bf Advect Base Pressure}$[p_0^{n}, w_0^{\nph}, \etarho^{n+\myhalf}]$ 
$\rightarrow [p_0^{n+1}, \psi^{n+\myhalf}]$.

>>>>

\item We eliminated {\bf Advect Base Pressure} entirely, and instead directly
enforce HSE after {\bf Correct Base}.  {\bf Advect Base Pressure} was just a fancy
way of enforcing HSE anyway, so we just compute the new pressure directly.

@@

@@

@@

\item Update $p_0$ to enforce hydrostatic equilbrium, $\nabla p_0^{n+1,\star} = -\rho_0^{n+1,\star} g$

\item Compute $\psi^{\nph,\star}$

@@

\item Update $p_0$ to enforce hydrostatic equilbrium, $\nabla p_0^{n+1} = -\rho_0^{n+1} g$

\item Compute $\psi^{\nph}$
